No Evidence for the Aquarius Co-Moving Group \\Resulting from a Disrupted Classical Globular Cluster\altaffilmark{1}

### 2013-02-05 2012-aqs/draft-aqs.tex
Incorporated Keller comments

% [DONE] Na/O subplots
% [DONE] Na/O comparison with halo
% [DONE] Mg/Al subplots
% - Ni/Na plane plot
% - Add standard stars to observations table
% - Add standard stars chemical abundances
% - Add in-line text referencing standard star chemical abundances
% - Uncertainties analysis
% [DONE] Equivalent widths significant figures.
% - Strontium?
% - Carbon?
% - Distance calculations revision
% - Transverse motions table
% - Transverse motions text
% - Orbital energies plot
% - Minor merger text
% - Conclusions

% Casey, Keller, Alves-Brito, Frebel, Da Costa, Schlaufman, Karakas, Heather, QinQin, Freeman

@@

% Identification of the aquarius stream
Using these data, \citet{williams;et-al_2011} identified a co-moving group of nearby ($0.5\,\mbox{kpc} \lesssim d \lesssim 10\,\mbox{kpc}$) stars in the vicinity of the Aquarius constellation $(l, b) = (60\,^\circ, -55\,^\circ)$. Thus, the co-moving group was named the Aquarius stream. The artefact is most apparent when examining velocities against galactic latitude for stars within $-70\,^\circ < b < -50\,^\circ$. \citet{williams;et-al_2011} employed a selection criteria of $-250\,\mbox{km s}^{-1} < V_{\rm hel} < -150\,\mbox{km s}^{-1}$, $30\,^\circ < l < 75\,^\circ$ and $J > 10.3$ to maximize the contrast between the stream and background, identifying 15 candidates in the process. The average heliocentric velocity of these members was found to be $V_{\rm hel} = -199\,\mbox{km s}^{-1}$, with a dispersion of 27\,km s$^{-1}$. The radial velocity uncertainties provided by the RAVE catalog are described to be $\sim$2\,km s$^{-1}$, so the wide kinematic distribution appears to be real.

@@

The Aquarius stream has a metallicity of $\mbox{[Fe/H]} \sim -1.0$, slightly more metal-rich than halo stars at the same distance. \citet{williams;et-al_2011} found the stream to have an average of $\mbox{[M/H]} = -1.0 \pm 0.4$, compared to $\mbox{[M/H]} = -1.1 \pm 0.6$ for background stars after the same selection cuts had been employed. Of the 12 Aquarius stars in the \citet{williams;et-al_2011} discovery sample with stellar parameters, the metallicity range is wide: between --2.02 and --0.33 dex. Spectroscopic observations of high resolution with high $S/N$ are necessary to accurately characterize the stream's metallicity distribution.

@@

In addition to ascertaining stellar parameters, \citet{wylie-de-boer;et-al_2012} measured elemental abundances for the Aquarius stream stars -- the only study to do so until now. The authors primarily focussed on light elements: Na, O, Ni, Mg, and Al. Chemical patterns in these light elements arise as natural consequences of nucleosynthetic processes in massive stars. These patterns have been repeatedly observed in globular clusters. Specifically, an anti-correlation between sodium and oxygen content appears ubiquitous to globular clusters. Originally this relationship was thought to arise from internal mixing along the giant branch. However, dwarf globular cluster stars were found to exhibit strong Na-enhancement and O-depletion, contrary to what would be expected if the Na-O anti-correlation was purely a result of internal mixing. It is well known now that photospheric abundance variations resulting from internal mixing are limited to carbon, nitrogen and lithium. Additionally, light element variations can be explained by classic nucleosynthetic pathways, albeit extreme temperatures are necessary for such relationships to arise \--- much higher than would reasonably be expected in globular cluster stars. Several descriptions for an astrophysical site that would permit such nucleosynthetic processes have been hypothesized, including massive intermediate-mass Asymptotic Giant Branch (AGB) binary stars \citep{de_mink;et-al_2009} and fast-rotating massive stars \citep{decressin;et-al_2007}. While the exact formation site is still under debate, the chemical relationship is well-established empirically. The Na-O pattern provides the best chemical evidence that their chemical enrichment history has been dominated by Sn \textsc{ii} events and that those stars formed in a globular cluster-like environment.

@@

\\ \multicolumn{11}{c}{Standard Stars} \\ \hline \\
HD 41667		& 06:05:03.7 & $-$32:59:36.8	& 2011-03-13	& 1.005	& \dots & \dots & \dots & 314.4	& \dots & 0.8 \\
HD 142948		& 16:00:01.6 & $-$53:51:04.1	& 2011-03-14	& 1.107	& \dots & \dots & \dots & 6.8		& \dots & 0.4 \\

@@

@@

The most complete sample of Aquarius stream stars is presented in the discovery paper of \citet{williams;et-al_2011}. Our sample includes five stars: four common to the \citet{wylie-de-boer;et-al_2012} study, and an additional candidate from the original \citet{williams;et-al_2011} sample. The supplementary star, J2306265-085103, was observed by the RAVE survey but had a $S/N$ ratio too low for stellar parameters to be accurately determined. All program stars were observed in July 2011 in good seeing at low airmass (Table \ref{tab:observations}), and X additional standard stars were observed in March 2011. All observations were taken using a 1.0'' slit, providing a spectral resolution of $\mathcal{R} = 28,000$ in the blue arm and $\mathcal{R} = 22,000$ in the red arm. The total exposure times for our program stars varied to ensure a $S/N$ ratio in excess of 100\,pixel$^{-1}$ at 600\,nm.

% what spectral resolution in the blue, what resolution in the red

@@

The equivalent widths for all absorption lines were measured automatically using software written for this study. Given the rest wavelength and an initial guess of the FWHM, a Gaussian profile is iteratively fitted to the absorption line. At the same time, the local continuum is found within 20\,\AA{} either side of the rest wavelength using a second-order polynomial. Measuring the local continuum ensures any errors in our initial normalisation or order-stitching do not propagate through to our equivalent width measurements. When determining the local continuum, any neighbouring group of pixels that deviate significantly ($>$2-$\sigma$) from the local continua either belong to a persistent cosmic ray hit, or they are trough points of a neighbouring absorption profile. We attempt to fit a Gaussian profile to each group of deviating pixels, using the current best estimate for the local continuum. If a Gaussian profile is successfully fitted to the deviating group and its surrounding pixels, we assume the outlier points belong to an absorption line and all pixels belonging to that profile are excluded from the continuum determination.

@@

\begin{deluxetable*}{lcccccccccccccc}[h!]
\tablecolumns{2}
\tabletypesize{\scriptsize}
\tablecaption{Stellar Parameters\label{tab:stellar-parameters}}
\tablehead{
	\colhead{Designation} &
	\colhead{$T_{\rm eff}$} &
	\colhead{$\log{g}$} &
	\colhead{$v_t$} &
	\colhead{[Fe/H]} & 
	\colhead{$T_{\rm eff}$} &
	\colhead{$\log{g}$} &
	\colhead{$v_t$} &
	\colhead{[Fe/H]} &
	\colhead{Source} \\
	& (K) & (dex) & (km\,s$^{-1}$) & (dex) & (K) & (dex) & (km s$^{-1}$) & (dex) 
}
\startdata
\multicolumn{10}{c}{Standard Stars} \\
\cline{1-10} \\
HD41667			& 4630	& 1.70	& 1.66 	& --1.21
				& 4605	& 1.88	& 1.44	& --1.16
				& \citet{gratton;et-al_2000} \\
HD44007			& 4790	& 1.78	& 1.63	& --1.80
				& 4850	& 2.00 	& 2.20	& --1.71
				& \citet{fulbright_2000} \\
HD142948		& 4950	& 2.19	& 1.78	& --0.79
				& 4713 	& 2.17 	& 1.38	& --0.77
				& \citet{gratton;et-al_2000} \\
\\
\multicolumn{10}{c}{Program Stars} \\
\cline{1-10} \\
C2225316-14437	& 4325				& 1.26				& 1.78				& --1.26	
				& 4235 $\pm$ 118 	& 1.45 $\pm$ 0.21	& 1.96 $\pm$ 0.11 	& --1.20 $\pm$ 0.14 
				& \citet{wylie-de-boer;et-al_2012} \\
C2306265-085103	& 4170	& 0.85	& 1.81 	& --1.17
				& \dots	& \dots	& \dots	& \dots
				& \dots \\	
J221821-183424	& 4590				& 0.90				& 1.91				& --1.61
				& 4395 $\pm$ 205 	& 1.45 $\pm$ 0.35 	& 1.96 $\pm$ 0.18 	& --1.15 $\pm$ 0.21
				& \citet{wylie-de-boer;et-al_2012} \\
J223504-152834	& 4590				& 2.15 				& 1.45				& --0.68
				& 4597 $\pm$ 158 	& 2.40 $\pm$ 0.14 	& 1.47 $\pm$ 0.07 	& --0.98 $\pm$ 0.17
				& \citet{wylie-de-boer;et-al_2012} \\
J223811-104126	& 5140				& 2.96				& 1.33				& --1.45
				& 5646 $\pm$ 147 	& 4.60 $\pm$ 0.15 	& 1.09 $\pm$ 0.11 	& --1.20 $\pm$ 0.20
				& \citet{wylie-de-boer;et-al_2012} 
\enddata

@@

@@

The effective temperatures published for all of our stars in Table \ref{sec:stellar-parameters} have been derived spectroscopically. As a consistency check for our spectroscopic temperatures, we have estimated effective temperatures using infrared photometry from the 2MASS catalog and empirical $T_{\rm eff}$-colour relationships. The $J-K$ color has been employed for these calculations because it has the least dependence on metallicity.

@@

Although all of our candidates are giant stars, two different $T_{\rm eff}$-colour relationships have been employed: the \citet{alonso;et-al_1999} calibration for giants, and the \citet{casagrande;et-al_2010} calibration for dwarfs and sub-giants. All photometrically-derived temperatures are listed in \ref{tab:photometric-temperatures}. The \citet{alonso;et-al_1999} $J-K$ scale is insensitive to metallicity effects, and is in good agreement with our spectroscopic temperatures. For the \citet{casagrande;et-al_2010} $J-K$ relationship, which has a slight metallicity dependency, we have utilized the spectroscopically-derived [Fe/H] values shown in Table \ref{tab:stellar-parameters}.

@@

Given the line list employed in the \citet{wylie-de-boer;et-al_2012} study, the overall data quality and the lack of suitable iron lines available for analysis, it appears the Aquarius stream stars conspired to present a tight metallicity distribution function of $\sigma(\mbox{Fe/H}) = 0.10$\,dex. When viewed in light of enhanced [Ni/Fe], [Na/Fe] abundance ratios, this chemistry is suggestive of a globular cluster origin. Our analysis of high-resolution spectra with high $S/N$ reveals a much broader metallicity distribution for the stream. With just five stars \--- if we assume all our candidates are members \--- we find the stream metallicity varies from $\mbox{[Fe/H]} = -0.65$ to --1.60\,dex. Although this is a small sample, we find the calculated median abundance and standard deviation to be $\mbox{[Fe/H]} = -1.26 \pm 0.32$\,dex.

@@

\begin{figure*}[t!]
	\includegraphics[width=\textwidth]{./figures/aquarius-vhel-feh.pdf}
	\caption{Helocentric velocities and metallicities for Aquarius candidates in this sample. The measurements found by \citet{williams;et-al_2011} (green squares) and \citet{wylie-de-boer;et-al_2012} (blue triangles) are shown, and stars are linked by dashed lines. \citet{wylie-de-boer;et-al_2012} used the \citet{williams;et-al_2011} velocities, which is why their measurements are coincident on the abscissa.}
	\label{fig:aquarius-vhel-feh}
\end{figure*}

@@

Stars originating in dwarf spheroidal galaxies and globular clusters have very different chemical enrichment environments. Consequently, they exhibit chemistry that reflects their nucleosynthetic antiquity. Dwarf spheroidal stars do not demonstrate enhanced sodium or nickel content with respect to iron, as there has been a relatively negligible linage of massive stars undergoing supernova. In contrast, globular cluster stars do have elevated [Na/Fe], [Ni/Fe] signatures. This sharp contrast between dwarf spheroidal and globular cluster star chemistry is illustrated in Figure \ref{fig:na-ni}. Given the extended star formation within the Milky Way disk, globular cluster stars and disk stars are indiscernible in the Na/Ni plane: they both show an extended contribution of massive stars.

>>>>

% [DONE] Na/O subplots
% [DONE] Na/O comparison with halo
% [DONE] Mg/Al subplots
% - Ni/Na plane plot
% - Add standard stars to observations table
% - Add standard stars chemical abundances
% - Add in-line text referencing standard star chemical abundances
% - Uncertainties analysis
% [DONE] Equivalent widths significant figures.
% - Strontium
% - Carbon
% - Distance calculations revision with B-V (if available) instead of (J-K)
% - Transverse motions table
% - Transverse motions text
% - Orbital energies plot w.r.t Zolotov simulations
% - Minor merger text
% - Conclusions

% Casey, Keller, Alves-Brito, Frebel, Da Costa, Schlaufman, Karakas, Jacobson, Yu, Freeman

@@

% Identification of the aquarius stream
Using these data, \citet{williams;et-al_2011} identified a co-moving group of nearby ($0.5\,\mbox{kpc} \lesssim d \lesssim 10\,\mbox{kpc}$) stars in the vicinity of the Aquarius constellation $(l, b) = (60\,^\circ, -55\,^\circ)$. Thus, the co-moving group was named the Aquarius stream. The group is most apparent when examining velocities against galactic latitude for stars within $-70\,^\circ < b < -50\,^\circ$. \citet{williams;et-al_2011} employed a selection criteria of $-250\,\mbox{km s}^{-1} < V_{\rm hel} < -150\,\mbox{km s}^{-1}$, $30\,^\circ < l < 75\,^\circ$ and $J > 10.3$ to maximize the contrast between the stream and background, identifying 15 candidates in the process. The average heliocentric velocity of these members was found to be $V_{\rm hel} = -199\,\mbox{km s}^{-1}$, with a dispersion of 27\,km s$^{-1}$. The radial velocity uncertainties provided by the RAVE catalog are described to be $\sim$2\,km s$^{-1}$, so the wide kinematic distribution appears to be real.

@@

RAVE observations suggest the Aquarius stream has a metallicity of $\mbox{[Fe/H]} \sim -1.0$, slightly more metal-rich than halo stars at the same distance. \citet{williams;et-al_2011} found the stream to have an average of $\mbox{[M/H]} = -1.0 \pm 0.4$, compared to $\mbox{[M/H]} = -1.1 \pm 0.6$ for background stars after the same selection cuts had been employed. Of the 12 Aquarius stars in the \citet{williams;et-al_2011} discovery sample with stellar parameters, the metallicity range is wide: between --2.02 and --0.33 dex. Spectroscopic observations of high resolution with high $S/N$ are necessary to accurately characterize the stream's metallicity distribution.

@@

In addition to ascertaining stellar parameters, \citet{wylie-de-boer;et-al_2012} measured elemental abundances for the Aquarius stream stars -- the only study to do so until now. The authors primarily focussed on light elements: Na, O, Ni, Mg, and Al. Chemical patterns in these light elements arise as natural consequences of nucleosynthetic processes in massive stars. These patterns have been repeatedly observed in globular clusters. Specifically, an anti-correlation between sodium and oxygen content appears ubiquitous to globular clusters. While the exact formation site is still under debate, the chemical relationship is well-established empirically. The Na-O pattern provides the best chemical evidence that their chemical enrichment history has been dominated by Type \textsc{ii} Supernova (SN) events and that those stars formed in a globular cluster-like environment.

% The following text was placed before 'While the ...'
%Originally this relationship was thought to arise from internal mixing along the giant branch. However, dwarf globular cluster stars were found to exhibit strong Na-enhancement and O-depletion, contrary to what would be expected if the Na-O anti-correlation was purely a result of internal mixing. It is well known now that photospheric abundance variations resulting from internal mixing are limited to carbon, nitrogen and lithium. Additionally, light element variations can be explained by classic nucleosynthetic pathways, albeit extreme temperatures are necessary for such relationships to arise \--- much higher than would reasonably be expected in globular cluster stars. Several descriptions for an astrophysical site that would permit such nucleosynthetic processes have been hypothesized, including massive intermediate-mass Asymptotic Giant Branch (AGB) binary stars \citep{de_mink;et-al_2009} and fast-rotating massive stars \citep{decressin;et-al_2007}.

@@

\\ \multicolumn{11}{c}{Standard Stars} \\ \hline \\
HD 41667		& 06:05:03.7 & $-$32:59:36.8	& 2011-03-13	& 1.005	& \dots & \dots & \dots & 314.4	& \dots & 0.8 \\
HD 44007		& 06:18:48.6 & $-$14:50:44.2 	& 2011-03-13	& 1.033	& \dots & \dots & \dots & --185.9	& 162.9 & 0.6 \\
HD 136316		& 15:22:17.2 & $-$53:14:13.9	& 2011-03-14	& 1.118	& \dots & \dots & \dots & 61.0		& --37.6 & 0.4 \\
HD 141531		& 15:49:16.9 & \phn\.09:36:42.5		& 2011-03-14	& 1.309	& \dots & \dots & 350	 & 17.7		& 2.8	& 0.1 \\
HD 142948		& 16:00:01.6 & $-$53:51:04.1	& 2011-03-14	& 1.107	& \dots & \dots & \dots & 6.8		& \dots & 0.4 \\

@@

%HD 136316 % F giant, -1.8, Gratton 2000+, has Na, O abundances
%HD 141531 % F giant, -1.6, Gratton 2000+, has Na, O abundances
%HD 44007 % G giant, -1.50, lots of references

% Hd 141431		: -0.96, -1.03 +/- 0.78 (MEK)

@@

The most complete sample of Aquarius stream stars is presented in the discovery paper of \citet{williams;et-al_2011}. Our sample includes five stars: four common to the \citet{wylie-de-boer;et-al_2012} study, and an additional candidate from the original \citet{williams;et-al_2011} sample. The supplementary star, J2306265-085103, was observed by the RAVE survey but had a $S/N$ ratio too low for stellar parameters to be accurately determined. All program stars were observed in July 2011 in good seeing at low airmass (Table \ref{tab:observations}), and five additional standard stars were observed in March 2011. All observations were taken using a 1.0'' slit, providing a spectral resolution of $\mathcal{R} = 28,000$ in the blue arm and $\mathcal{R} = 22,000$ in the red arm. The total exposure times for our program stars varied to ensure a $S/N$ ratio in excess of 100\,pixel$^{-1}$ at 600\,nm.

@@

The equivalent widths for all absorption lines were measured automatically using software written for this study. Given the rest wavelength and an initial guess of the FWHM, a Gaussian profile is iteratively fitted to the absorption line. At the same time, the local continuum is found within 10\,\AA{} either side of the rest wavelength using a second-order polynomial. Measuring the local continuum ensures any errors in our initial normalisation or order-stitching do not propagate through to our equivalent width measurements. When determining the local continuum, any neighbouring group of pixels that deviate significantly ($>$2-$\sigma$) from the local continua either belong to a persistent cosmic ray hit, or they are trough points of a neighbouring absorption profile. We attempt to fit a Gaussian profile to each group of deviating pixels, using the current best estimate for the local continuum. If a Gaussian profile is successfully fitted to the deviating group and its surrounding pixels, we assume the outlier points belong to an absorption line and all pixels belonging to that profile are excluded from the continuum determination.

@@

\begin{deluxetable*}{lcccccccccccccc}[h!]
\tablecolumns{2}
\tabletypesize{\scriptsize}
\tablecaption{Stellar Parameters\label{tab:stellar-parameters}}
\tablehead{
	\colhead{Designation} &
	\colhead{$T_{\rm eff}$} &
	\colhead{$\log{g}$} &
	\colhead{$v_t$} &
	\colhead{[Fe/H]} & 
	\colhead{$T_{\rm eff}$} &
	\colhead{$\log{g}$} &
	\colhead{$v_t$} &
	\colhead{[Fe/H]} &
	\colhead{Source} \\
	& (K) & (dex) & (km\,s$^{-1}$) & (dex) & (K) & (dex) & (km s$^{-1}$) & (dex) 
}
\startdata
\multicolumn{10}{c}{Standard Stars} \\
\cline{1-10} \\
HD41667			& 4630	& 1.70	& 1.66 	& --1.21
				& 4605	& 1.88	& 1.44	& --1.16
				& \citet{gratton;et-al_2000} \\
HD44007			& 4790	& 1.78	& 1.63	& --1.80
				& 4850	& 2.00 	& 2.20	& --1.71
				& \citet{fulbright_2000} \\
HD142948		& 4950	& 2.19	& 1.78	& --0.79
				& 4713 	& 2.17 	& 1.38	& --0.77
				& \citet{gratton;et-al_2000} \\
\\

\multicolumn{10}{c}{Program Stars} \\
\cline{1-10} \\
C2225316-14437	& 4325				& 1.26				& 1.78				& --1.26	
				& 4235 $\pm$ 118 	& 1.45 $\pm$ 0.21	& 1.96 $\pm$ 0.11 	& --1.20 $\pm$ 0.14 
				& \citet{wylie-de-boer;et-al_2012} \\
C2306265-085103	& 4170	& 0.85	& 1.81 	& --1.17
				& \dots	& \dots	& \dots	& \dots
				& \dots \\	
J221821-183424	& 4590				& 0.90				& 1.91				& --1.61
				& 4395 $\pm$ 205 	& 1.45 $\pm$ 0.35 	& 1.96 $\pm$ 0.18 	& --1.15 $\pm$ 0.21
				& \citet{wylie-de-boer;et-al_2012} \\
J223504-152834	& 4590				& 2.15 				& 1.45				& --0.68
				& 4597 $\pm$ 158 	& 2.40 $\pm$ 0.14 	& 1.47 $\pm$ 0.07 	& --0.98 $\pm$ 0.17
				& \citet{wylie-de-boer;et-al_2012} \\
J223811-104126	& 5140				& 2.96				& 1.33				& --1.45
				& 5646 $\pm$ 147 	& 4.60 $\pm$ 0.15 	& 1.09 $\pm$ 0.11 	& --1.20 $\pm$ 0.20
				& \citet{wylie-de-boer;et-al_2012} 
\enddata

@@

%HD 136316 % F giant, -1.8, Gratton 2000+, has Na, O abundances [DONE]
%HD 141531 % F giant, -1.6, Gratton 2000+, has Na, O abundances [DONE]
%HD 44007 % G giant, -1.50, lots of references

@@

The effective temperatures published for all of our stars in Table \ref{sec:stellar-parameters} have been derived spectroscopically. As a consistency check for our spectroscopic temperatures, we have estimated effective temperatures using infrared photometry from the 2MASS catalog and empirical $T_{\rm eff}$-color relationships. The $J-K$ color has been employed for these calculations because it has the least dependence on metallicity.

@@

Although all of our candidates are giant stars, two different $T_{\rm eff}$-color relationships have been employed: the \citet{alonso;et-al_1999} calibration for giants, and the \citet{casagrande;et-al_2010} calibration for dwarfs and sub-giants. All photometrically-derived temperatures are listed in \ref{tab:photometric-temperatures}. The \citet{alonso;et-al_1999} $J-K$ scale is insensitive to metallicity effects, and is in good agreement with our spectroscopic temperatures. For the \citet{casagrande;et-al_2010} $J-K$ relationship, which has a slight metallicity dependency, we have utilized the spectroscopically-derived [Fe/H] values shown in Table \ref{tab:stellar-parameters}.

@@

Given the line list employed in the \citet{wylie-de-boer;et-al_2012} study, the overall data quality and the lack of suitable iron lines available for analysis, it appears the Aquarius stream stars conspired to present a tight metallicity distribution function of $\sigma(\mbox{Fe/H}) = 0.10$\,dex. When viewed in light of enhanced [Ni/Fe], [Na/Fe] abundance ratios, this chemistry is suggestive of a globular cluster origin. Our analysis of high-resolution spectra with high $S/N$ reveals a much broader metallicity distribution for the stream. With just five stars we find the stream metallicity varies from $\mbox{[Fe/H]} = -0.65$ to --1.60\,dex. Although this is a small sample, we find the calculated median abundance and standard deviation to be $\mbox{[Fe/H]} = -1.26 \pm 0.32$\,dex.

@@

\begin{figure*}[t!]
	\includegraphics[width=\textwidth]{./figures/aquarius-vhel-feh.pdf}
	\caption{Heliocentric velocities and metallicities for Aquarius candidates in this sample. The measurements found by \citet{williams;et-al_2011} (green squares) and \citet{wylie-de-boer;et-al_2012} (blue triangles) are shown, and stars are linked by dashed lines. \citet{wylie-de-boer;et-al_2012} used the \citet{williams;et-al_2011} velocities, which is why their measurements are coincident on the abscissa.}
	\label{fig:aquarius-vhel-feh}
\end{figure*}

@@

Stars originating in dwarf spheroidal galaxies and globular clusters have very different chemical enrichment environments. Consequently, both types of systems exhibit chemistry that reflects their nucleosynthetic antiquity. Dwarf spheroidal stars do not demonstrate enhanced sodium or nickel content with respect to iron, as there has been a relatively negligible linage of massive stars undergoing supernova. In contrast, globular cluster stars do have elevated [Na/Fe], [Ni/Fe] signatures. This sharp contrast between dwarf spheroidal and globular cluster star chemistry is illustrated in Figure \ref{fig:na-ni}. Given the extended star formation within the Milky Way disk, globular cluster stars and disk stars are indiscernible in the Na/Ni plane: they both show an extended contribution of massive stars.
